\begin{frame}{Rossman and Chance Applets}
    \begin{center}
        www.rossmanchance.com/applets/
    \end{center}
    \vspace{12pt}This website contains a collection of applets that may be helpful in conceptualizing some of the topics from class.
\end{frame}

\begin{frame}{Random Number Generator}
    \begin{center}
        www.rossmanchance.com/applets/RandomGen/GenRandom01.htm
    \end{center}
    \vspace{12pt}\begin{itemize}
        \item Generate random numbers with or without replacement.
        \item Suppose we gave everyone in the class a number.
        \item Then we can use the random number generator to choose random samples.
    \end{itemize}
\end{frame}

\begin{frame}{Descriptive Statistics}
    \begin{center}
        www.rossmanchance.com/applets/Dotplot.html
    \end{center}
    \vspace{12pt}\begin{itemize}
        \item Generate a random sample.
        \item See histograms, dotplots, and boxplots of your random sample.
        \begin{itemize}
            \item Change bin widths for histograms.
        \end{itemize}
        \item Check the mean, standard deviation, median, and IQR for your sample.
        \item You may also use your own data!
    \end{itemize}
\end{frame}

\begin{frame}{Monty Hall}
    \begin{center}
        www.rossmanchance.com/applets/MontyHall/Monty04.html
    \end{center}
    \vspace{12pt}This applet simulates the Monty Hall problem we discussed yesterday.
\end{frame}

\begin{frame}{Random Babies}
    \begin{center}
        www.rossmanchance.com/applets/randomBabies/RandomBabies.html
    \end{center}
    \vspace{12pt}\begin{itemize}
        \item This shows some number of babies being randomly assigned to families.
        \item It tracks the average number of correct matches.
        \item This and the Monty Hall applet are also demonstrations of the Law of Large Numbers.
    \end{itemize}
\end{frame}

\begin{frame}{Midterm}
    This concludes the material for the midterm.
    
    \vspace{12pt}Tomorrow we are moving on to Chapter 4!
\end{frame}

\begin{frame}{Questions?}
    Are there any questions you'd like answered before Monday?
\end{frame}